Waiting time analysis

### 2025-04-26 notebooks/21_model.qmd
update

```{julia}
using DrWatson
using Discontinuity
using Discontinuity: Alfven_current
using DataFramesMeta
using PlasmaFormulary: inertial_length
using SpaceDataModel: tryparse_datetime

@quickactivate
include("../src/main.jl")
```

```{julia}
using CSV
using DataFrames
using Unitful

"""
    read_sw_params_csv(file="jgra54158-sup-0001-supinfo.csv")

Reads the solar wind parameters CSV file and returns a DataFrame.
"""
function read_sw_params_csv(file=datadir("jgra54158-sup-0001-supinfo.csv"))
    df = CSV.read(file, DataFrame)
    @chain df begin
        @transform! @byrow begin
            :time = tryparse_datetime(String(:UTC))
            :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
            :V_KMPS = :V_KMPS * u"km/s"
        end
    end
    return df
end

@b read_sw_params_csv()

# jno_df = load()
```

@@

@chain jno_df_with_params begin
    @transform! begin

        :d_star = :d_star .* u"nT/s"
        :duration = :duration .* u"s"
        :V_KMPS = :V_KMPS .* u"km/s"
    end
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
        :j_Alfven_sw = Alfven_current.(:b_mag, :N_PROTONS_CC)
    end
    @transform! begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :j0_k_sw = @. abs(:d_star / :V_n_cross_sw / μ0) |> u"nA/m^2"
    end
    @transform! begin
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :j0_k_sw_norm = @. :j0_k_sw / :j_Alfven_sw |> NoUnits
    end
end
```

>>>>

```{julia}
using Discontinuity
using Discontinuity: Alfven_current
using PlasmaFormulary: inertial_length
@quickactivate
include("../src/main.jl")
```

```{julia}
using DrWatson: datadir
using CSV
using DataFrames, DataFramesMeta
using Unitful
using SpaceDataModel: parse_doy_datetime

"""Reads the solar wind parameters CSV file and returns a DataFrame."""
function read_sw_params_csv(file=datadir("jgra54158-sup-0001-supinfo.csv"))
    df = CSV.read(file, DataFrame)
    @chain df begin
        @transform! @byrow begin
            :time = parse_doy_datetime(:UTC)
            :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
            :V_KMPS = :V_KMPS * u"km/s"
        end
    end
    return df
end

jno_sw_params = read_sw_params_csv()
```

@@

@chain jno_df_with_params begin
    @transform! begin
        :d_star = :d_star .* u"nT/s"
        :duration = :duration .* u"s"
        :V_KMPS = :V_KMPS .* u"km/s"
    end
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
        :j_Alfven_sw = Alfven_current.(:b_mag, :N_PROTONS_CC)
    end
    @transform! begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :j0_k_sw = @. abs(:d_star / :V_n_cross_sw / μ0) |> u"nA/m^2"
    end
    @transform! begin
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :j0_k_sw_norm = @. :j0_k_sw / :j_Alfven_sw |> NoUnits
    end
end
```
